Supplementary Materials for ``Frustration shapes multi-channel Kondo physics: a star graph perspective"

### 2023-01-13 MCK-manuscript/MCK-manuscript.tex
sir's changes

The derivation of the RG equation for the over-screened regime \((2S < K)\) of the spin-\(S\)-impurity \(K\)-channel Kondo problem is shown in detail in the Supplementary Materials~\cite{SM}.
On decoupling circular isoenergetic shells at energies \(D_{(j)}\), the change in the Kondo coupling at the \(j^\mathrm{th}\) RG step, \(\Delta {\mathcal{J}}_{(j)}\), is given by
\begin{eqnarray}
	\Delta {\mathcal{J}}_{(j)} = -\frac{{\mathcal{J}}_{(j)}^2 \mathcal{N}_{(j)}}{\omega_{(j)} - \frac{D_{(j)}}{2} + \frac{{\mathcal{J}}_{(j)}}{4}}\left( 1 - \frac{1}{2}\rho {\mathcal{J}}_{(j)} K \right)~, 
\end{eqnarray}
where \(\mathcal{N}_{(j)}\) is the number of electronic states at the energy shell \(D_{(j)}\). We work in the low quantum fluctuation regime \(\omega_{(j)} < \frac{D_{(j)}}{2}\). There are three fixed points of the RG equation. One arises from the vanishing of the denominator, and was present in the single-channel Kondo RG equation as well \cite{kondo_urg}. As shown there, this fixed-point goes to \({\mathcal{J}}^* = \infty\) as the bare bandwidth of the conduction electrons is made large. The other fixed point is the trivial one at \({\mathcal{J}}^* = 0\). The third fixed point is reached when the numerator vanishes: \({\mathcal{J}}^* = \frac{2}{K \rho}\) \cite{Gan_mchannel_1994,Kogan_2018,Kuramoto1998,Noz_blandin_1980}. Only the intermediate fixed point is found to be stable. This is consistent with results from Bethe ansatz calculations~\cite{Tsvelick_Weigmann_mchannel_1984,andrei_destri_1984,zarand_costi_2002,andrei_jerez_1995,Tsvelick_1985,Tsvelick1984}, CFT calculations~\cite{affleck_1991_overscreen,affleck1993exact,affleck_ludwig_1991}, bosonization treatments~\cite{emery_kivelson,vondelft_prl_1998} and NRG analysis~\cite{pang_cox_1991,mitchell_bulla_2014}.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.45\textwidth]{rgflow.pdf}
	\caption{The three fixed points of the over-screened RG equation. Only the intermediate one is stable.}
	\label{rg_flow}
\end{figure}

@@

Departure from single-channel behaviour is most apparent in the presence of the highly polarised states \(\ket{J^z=\pm \frac{K-1}{2}}\) in the ground-state spectrum,
\begin{eqnarray}
	\ket{J^z=\sigma \frac{K-1}{2}} =& \frac{1}{\sqrt{1 + K}} \ket{\sigma}_d\otimes\ket{S^z=\sigma(\frac{K}{2}-1)} \nonumber\\
					&- \frac{\sqrt K}{\sqrt{1 + K}}\ket{\bar\sigma}_d\otimes\ket{S^z=\sigma\frac{K}{2}},
\end{eqnarray}
where \(\sigma=\pm 1\) and \(\ket{\sigma}_d\) represents the up and down configurations of the impurity spin and \(\ket{S^z}\) represents the configuration of the bath spins. These states lead to large unquenched magnetisation at zero temperatures. These states lead to singular behaviour of the impurity magnetisation in vanishing field, \(m(h=0^\pm)\). In the presence of a field, the ground-state becomes unique: \(\ket{\psi}_\mathrm{gs}(h) = \theta(h)\ket{J^z=\frac{K-1}{2}} + \theta(-h)\ket{J^z=-\frac{K-1}{2}}\), and the impurity magnetisation can be calculated from the state:
\begin{eqnarray}
	m(h=0^\pm) &= \theta(h)\bra{J^z=\frac{K-1}{2}} S_d^z \ket{J^z=\frac{K-1}{2}} \nonumber\\
		   &+ \theta(-h)\bra{J^z=-\frac{K-1}{2}}S_d^z\ket{J^z=-\frac{K-1}{2}}\nonumber\\
	&= \pm  \frac{1}{2} \frac{1-K}{1 + K}\label{imp-magnetisation}~.
\end{eqnarray}

@@

The magnetization is therefore discontinuous as \(h\to 0\) for \(K>1\). The non-analyticity occurs because the magnetic field is able to flip the \(J^z=\pm (K-1)/2\) state into the state of the opposite magnetisation. This available space for scattering is simply the frustration that we discussed earlier. Indeed, we have checked (see Fig.~\ref{mag_crit}) by diagonalising numerically the star graph Hamiltonian that the non-analyticity exists for all \(\delta \neq 0\), where \(\delta = \frac{K}{2} - S_{d}\) is the deviation from exact screening.

These polarised states can also be used to obtain the scattering phase shift suffered by the conduction channels at the Fermi surface. As shown in the Supplementary Materials~\cite{SM}, the impurity-bath hybdridisation in the polarised states contribute an excess charge of \(n_\mathrm{exc}^{(l)} = 1/K\) to each conduction channel. Following Friedel's sum rule, this leads to a total scattering phase shift of \(\pi/K\) for each channel:
\begin{eqnarray}\label{phase-stargraph}
	\delta^{(l)} = \pi n_\mathrm{exc}^{(l)} = \frac{\pi}{K}, ~ ~ l \in \left[1, K\right] 
\end{eqnarray}
For \(K > 1\), each channel therefore experiences an unrenormalised phase shift of value between \(0\) and \(\pi\) that, as we will show in a later section, is responsible for the non-Fermi liquid behaviour. For example, we will show that this phase shift are linked to the critical non-Fermi liquid exponents of thermodynamic quantities at the fixed point. Right now, some evidence of this role of the phase shift can be provided through its relation to the vanishing field impurity magnetisation \(m\) obtained in eq.~\ref{imp-magnetisation}:
\begin{eqnarray}\label{magnetisation-phase}
	m(h=0^\pm) = \pm \frac{1}{2} \frac{\delta^{(l)} - \pi}{\delta^{(l)} + \pi}~.
\end{eqnarray}
When the phase shift \(\delta^{(l)}\) acquires a fractional value (in units of \(\pi\)), the impurity magnetisation also becomes fractional (in units of \(\frac{1}{2}\)). This shows that the "unrenormalised" phase shift value \(0 < \delta^{(l)} < \pi\)~\cite{anderson_1990} is at the heart of the quantum frustration present in the MCK problem, and leads, as we will see later, to a dramatic change in the ground-state wavefunction of the remaining degrees of freedom as the impurity is introduced, producing the well-known orthogonality catastrophe~\cite{anderson1967infrared,varma2002singular}.

@@

{\color{blue}We show in the Supplementary Materials~\cite{SM} that this orthogonality catastrophe can also be understood as a drastic change in the wavefunction and its quantum numbers. Upon taking account of the hopping between the star graph and the \(k-\)states of the conduction bath, the full ground-state \(\ket{\psi_-^{(l)}}\) and low-lying excited states \(\ket{\psi_+^{(l)}}\), in the \(l^\text{th}\) channel, take the form:
\begin{equation}\begin{aligned}
\ket{\psi_\pm^{(l)}} = \frac{1}{\sqrt 2}\left(\ket{\chi_{\frac{-1}{2}}}\otimes\ket{e_\uparrow^{(l)}} \pm \ket{\chi_{\frac{1}{2}}}\otimes\ket{e_\downarrow^{(l)}}\right)~,
\end{aligned}\end{equation}
where \(\ket{\chi_{\frac{\sigma}{2}}} = \frac{1}{\sqrt 6}\left( \ket{\sigma,\sigma,\bar\sigma} + \ket{\sigma,\bar\sigma,\sigma} -2\ket{\bar\sigma,\sigma,\sigma} \right),~ \sigma=\pm 1\) are the ground-states of the two-channel star graph, and \(\ket{e_\sigma^{(l)}} \equiv e^\dagger_{\sigma,(l)}\ket{\phi} = \sum_{k\in\text{FS}}c^\dagger_{k\sigma,(l)}\ket{\phi}\) are gapless excitations close to the Fermi surface (FS) \(\ket{\phi}\). We can now calculate the residue for scattering processes of the form \(e^\dagger_{\sigma,(l)} e_{\bar\sigma,(l)}\), in the new ground-state and excited state, and they are found to vanish:
\begin{equation}
	Z = |\braket{\psi_+^{(l)}| e^\dagger_{\uparrow,(l)} e_{\downarrow,(l)} | \psi_-^{(l)}}|^2 = \left|\bra{\psi_+^{(l)}}\left(\ket{\chi_{\frac{1}{2}}}\ket{e_\uparrow^{(l)}}\right)\right|^2 = 0
\end{equation}
This shows that the single-particle excitations are no longer long-lived, signaling the orthogonality catastrophe.

The orthogonality catastrophe in the infrared wavefunction points towards an ``unrenormalised" scattering phase shift in the conduction electrons at the fixed point. We have already seen from the zero mode approximation of the fixed point Hamiltonian that each channel suffers a phase shift of \(\delta^{(l)} = \pi/K\) (eq.~\ref{phase-stargraph}), which is non-zero but less than the unitarity limit. In this section, we will see how the phase shift guides the renormalisation group flow of the Kondo coupling \(J\). Following refs.~\cite{si_kotliar_1993,giamarchi_varma_1993,giamarchi_book}, the URG equation for \(J\) can be cast in the form
\begin{equation}\begin{aligned}
	\Delta {\mathcal{J}}_{(j)} = -\frac{{\mathcal{J}}_{(j)}^2 \mathcal{N}_{(j)}}{\omega_{(j)} - \frac{D_{(j)}}{2} + \frac{{\mathcal{J}}_{(j)}}{4}}\left( 1 - \frac{\rho {\mathcal{J}}_{(j)}}{2\delta^{(l)}/\pi} \right)~, 
\end{aligned}\end{equation}
The Kondo coupling continues to flow until the phase shift acquires the appropriate value: \(2\delta^{(l)}/\pi = \rho \mathcal{J}^* = 2/K\). Following eq.~\ref{magnetisation-phase}, this also leads to the fractional value of \(1/4\) for the impurity magnetisation \(m(0^+)\) in the spin-half two-channel Kondo model. The incommensurate values of both \(\delta^{(l)}\) and \(m(0^+)\) point to the frustrated nature of the problem and the absence of complete screening. These phase shifts also affect thermodynamic properties in the form of critical exponents in power-law behaviour. The impurity contributions to the specific heat linear coefficient \(\gamma = C_v/T\), the magnetic susceptibility \(\chi\) and the thermal entropy \(S\) take the forms~\cite{andrei_destri_1984,Tsvelick_Weigmann_mchannel_1984,affleck1993exact}
\begin{eqnarray}
	\gamma,\chi \sim \left( T/T_K \right)^\frac{1 - 2\delta^{(l)}/\pi}{1 + 2\delta^{(l)}/\pi}, ~ S \sim \ln \left[2\cos \frac{\delta^{(l)}}{1 + 2\delta^{(l)}/\pi}\right] 
\end{eqnarray}
}

>>>>

The derivation of the RG equation for the over-screened regime \((2S < K)\) of the spin-\(S\)-impurity \(K\)-channel Kondo problem is shown in detail in the Supplementary Materials~\cite{SM}.
On decoupling circular isoenergetic shells at energies \(D_{(j)}\), the change in the Kondo coupling at the \(j^\mathrm{th}\) RG step, \(\Delta {\mathcal{J}}_{(j)}\), is given by
\begin{eqnarray}
	\Delta {\mathcal{J}}_{(j)} = -\frac{{\mathcal{J}}_{(j)}^2 \mathcal{N}_{(j)}}{\omega_{(j)} - \frac{D_{(j)}}{2} + \frac{{\mathcal{J}}_{(j)}}{4}}\left( 1 - \frac{1}{2}\rho {\mathcal{J}}_{(j)} K \right)~, \label{mckRG}
\end{eqnarray}
where \(\mathcal{N}_{(j)}\) is the number of electronic states at the energy shell \(D_{(j)}\). We work in the low quantum fluctuation regime \(\omega_{(j)} < \frac{D_{(j)}}{2}\). There are three fixed points of the RG equation. One arises from the vanishing of the denominator, and was present in the single-channel Kondo RG equation as well \cite{kondo_urg}. As shown there, this fixed-point goes to \({\mathcal{J}}^* = \infty\) as the bare bandwidth of the conduction electrons is made large. The other fixed point is the trivial one at \({\mathcal{J}}^* = 0\). The third fixed point is reached when the numerator vanishes: \({\mathcal{J}}^* = \frac{2}{K \rho}\) \cite{Gan_mchannel_1994,Kogan_2018,Kuramoto1998,Noz_blandin_1980}. Only the intermediate fixed point is found to be stable. This is consistent with results from Bethe ansatz calculations~\cite{Tsvelick_Weigmann_mchannel_1984,andrei_destri_1984,zarand_costi_2002,andrei_jerez_1995,Tsvelick_1985,Tsvelick1984}, CFT calculations~\cite{affleck_1991_overscreen,affleck1993exact,affleck_ludwig_1991}, bosonization treatments~\cite{emery_kivelson,vondelft_prl_1998} and NRG analysis~\cite{pang_cox_1991,mitchell_bulla_2014}.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.45\textwidth]{rgflow.pdf}
	\caption{The three fixed points of the over-screened RG equation. Only the intermediate one is stable.}
	\label{rg_flow}
\end{figure}

@@

Departure from single-channel behaviour is most apparent in the presence of the highly polarised states \(\ket{J^z=\pm \frac{K-1}{2}}\) in the ground-state spectrum,
\begin{eqnarray}
	\ket{J^z=\sigma \frac{K-1}{2}} =& \frac{1}{\sqrt{1 + K}} \ket{\sigma}_d\otimes\ket{S^z=\sigma(\frac{K}{2}-1)} \nonumber\\
					&- \frac{\sqrt K}{\sqrt{1 + K}}\ket{\bar\sigma}_d\otimes\ket{S^z=\sigma\frac{K}{2}},
\end{eqnarray}
where \(\sigma=\pm 1\) and \(\ket{\sigma}_d\) represents the up and down configurations of the impurity spin and \(\ket{S^z}\) represents the configuration of the bath spins. These states lead to large unquenched magnetisation (\(m(h=0^\pm)\)) at zero temperatures
%. These states lead to singular behaviour of the impurity magnetisation 
that displays discontinuous behaviour in the limit of a vanishing field $h\to 0\pm$. This can be seen as follows. In the presence of a field, the ground-state becomes unique: \(\ket{\psi}_\mathrm{gs}(h) = \theta(h)\ket{J^z=\frac{K-1}{2}} + \theta(-h)\ket{J^z=-\frac{K-1}{2}}\), and the impurity magnetisation can be calculated from the state:
\begin{eqnarray}
	m(h=0^\pm) &= \theta(h)\bra{J^z=\frac{K-1}{2}} S_d^z \ket{J^z=\frac{K-1}{2}} \nonumber\\
		   &+ \theta(-h)\bra{J^z=-\frac{K-1}{2}}S_d^z\ket{J^z=-\frac{K-1}{2}}\nonumber\\
	&= \pm  \frac{1}{2} \frac{1-K}{1 + K}\label{imp-magnetisation}~.
\end{eqnarray}

@@

The magnetization is therefore discontinuous as \(h\to 0\pm\) for \(K>1\). The non-analyticity occurs because the magnetic field is able to flip the states with \(J^z= (K-1)/2\) into the state of the opposite magnetisation and vice versa. The available space for scattering is simply the frustration that we discussed earlier. Indeed, we have checked (see Fig.~\ref{mag_crit}) by diagonalising numerically the star graph Hamiltonian that the non-analyticity exists for all \(\delta \neq 0\), where \(\delta = \frac{K}{2} - S_{d}\) is the deviation from exact screening.

These polarised states can also be used to obtain the scattering phase shift suffered by the conduction channels at the Fermi surface. As shown in the Supplementary Materials~\cite{SM}, the impurity-bath hybdridisation in the polarised states contribute an excess charge of \(n_\mathrm{exc}^{(l)} = 1/K\) to each conduction channel. Following Friedel's sum rule, this leads to a total scattering phase shift of \(\pi/K\) for each channel:
\begin{eqnarray}\label{phase-stargraph}
	\delta^{(l)} = \pi n_\mathrm{exc}^{(l)} = \frac{\pi}{K}, ~ ~ l \in \left[1, K\right] 
\end{eqnarray}
For \(K > 1\), each channel therefore experiences an unrenormalised phase shift of value between \(0\) and \(\pi\) that, as we will show in a later section, is responsible for the non-Fermi liquid behaviour observed at the ICFP. For example, we will show that these phase shifts are linked to the critical non-Fermi liquid exponents of various thermodynamic quantities at the fixed point. That this phase shift is tied to the frustration that leads to incomplete Kondo screening at the ICFP can be evidenced 
%of this role of the phase shift can be provided 
through its relation to the impurity magnetisation \(m (h=0\pm)\) obtained in eq.~\ref{imp-magnetisation}:
\begin{eqnarray}\label{magnetisation-phase}
	m(h=0^\pm) = \pm \frac{1}{2} \frac{\delta^{(l)} - \pi}{\delta^{(l)} + \pi}~.
\end{eqnarray}
When the phase shift \(\delta^{(l)}\) acquires a fractional value (in units of \(\pi\)) at the ICFP, the impurity magnetisation also becomes fractional (in units of \(\frac{1}{2}\)). We will see shortly that this unrenormalised phase shift value of \(0 < \delta^{(l)} < \pi\)~\cite{anderson_1990} is also at the heart of 
%the quantum frustration present in the MCK problem, and leads, as we will see shortly, to 
an orthogonality catastrophe, i.e., a dramatic change in the ground-state wavefunction of the conduction bath degrees of freedom as the impurity is introduced among them~\cite{anderson1967infrared,varma2002singular}.

@@

Further, we argue below that the orthogonality catastrophe for the 2-channel problem can also be understood as a drastic change in the ground state and lowest-lying excited state wavefunctions and related quantum numbers. The detailed calculation has been shown in the Supplementary Materials~\cite{SM}. Upon taking account of the hopping between the star graph and the \(k-\)states of the conduction bath, the full ground-state \(\ket{\psi_-^{(l)}}\) and low-lying excited states \(\ket{\psi_+^{(l)}}\)  in the \(l^\text{th}\) channel  take the form:
\begin{equation}\begin{aligned}
\ket{\psi_\pm^{(l)}} = \frac{1}{\sqrt 2}\left(\ket{\chi_{-\frac{1}{2}}}\otimes\ket{e_\uparrow^{(l)}} \pm \ket{\chi_{\frac{1}{2}}}\otimes\ket{e_\downarrow^{(l)}}\right)~,
\end{aligned}\end{equation}
where \(\ket{\chi_{\frac{\sigma}{2}}} = \frac{1}{\sqrt 6}\left( \ket{\sigma,\sigma,\bar\sigma} + \ket{\sigma,\bar\sigma,\sigma} -2\ket{\bar\sigma,\sigma,\sigma} \right),~ \sigma=\pm 1\) are the ground-states of the two-channel star graph, and \(\ket{e_\sigma^{(l)}} \equiv e^\dagger_{\sigma,(l)}\ket{\phi} = \sum_{k\in\text{FS}}c^\dagger_{k\sigma,(l)}\ket{\phi}\) are gapless excitations close to the Fermi surface (FS) \(\ket{\phi}\). The residue for scattering processes of the form \(e^\dagger_{\sigma,(l)} e_{\bar\sigma,(l)}\) between the new ground and excited states is then found to vanish:
\begin{equation}
	Z = |\braket{\psi_+^{(l)}| e^\dagger_{\uparrow,(l)} e_{\downarrow,(l)} | \psi_-^{(l)}}|^2 = \left|\bra{\psi_+^{(l)}}\left(\ket{\chi_{\frac{1}{2}}}\ket{e_\uparrow^{(l)}}\right)\right|^2 = 0~.
\end{equation}
This shows that single-particle excitations (a signature of the local Fermi liquid associated with the single channel Kondo fixed point) are no longer long-lived, signalling the orthogonality catastrophe.

The orthogonality catastrophe in the infrared wavefunction arises from an unrenormalised scattering phase shift in the conduction electrons at the fixed point. We have already seen from the zero mode approximation of the fixed point Hamiltonian that each channel suffers a phase shift of \(\delta^{(l)} = \pi/K\) (eq.~\ref{phase-stargraph}), which is non-zero but less than the limit of unitarity. We will now see that this phase shift guides the renormalisation group flow of the Kondo coupling \(J\). Following refs.~\cite{si_kotliar_1993,giamarchi_varma_1993,giamarchi_book}, the URG equation for \(J\) (eq.\ref{mckRG}) can be recast in the form
\begin{equation}\begin{aligned}
	\Delta {\mathcal{J}}_{(j)} = -\frac{{\mathcal{J}}_{(j)}^2 \mathcal{N}_{(j)}}{\omega_{(j)} - \frac{D_{(j)}}{2} + \frac{{\mathcal{J}}_{(j)}}{4}}\left( 1 - \frac{\rho {\mathcal{J}}_{(j)}}{2\delta^{(l)}/\pi} \right)~.
\end{aligned}\label{scattphaseRG}\end{equation}
The Kondo coupling $J$ continues to flow under RG until it obtains a value dictated by the phase shift of the star graph: \(\rho \mathcal{J}^* = 2\delta^{(l)}/\pi = 2/K\). Following eq.~\ref{magnetisation-phase}, this also leads to the fractional value of \(1/4\) for the impurity magnetisation \(m(0^+)\) in the spin-half two-channel Kondo model. Indeed, the values of both \(\delta^{(l)}\) and \(m(0^+)\) point to the frustrated nature of the MCK problem and the absence of complete screening of the impurity moment at the ICFP. Importantly, the phase shifts \(\delta^{(l)}\) also affect the critical exponents of well-known algebraic behaviour of several thermodynamic properties at the ICFP. The impurity contributions to the specific heat linear coefficient \(\gamma = C_v/T\), the magnetic susceptibility \(\chi\) and the thermal entropy \(S\) take the forms~\cite{andrei_destri_1984,Tsvelick_Weigmann_mchannel_1984,affleck1993exact}
\begin{eqnarray}
	\gamma &\sim & \left( T/T_K \right)^\frac{1 - 2\delta^{(l)}/\pi}{1 + 2\delta^{(l)}/\pi} = \left( T/T_K \right)^\frac{K-2}{K+2}\sim \chi~,\nonumber\\ 
	S &\sim & \ln \left[2|\cos \left(\frac{\delta^{(l)}}{1 + 2\delta^{(l)}/\pi}\right)|\right]
	 = \ln \left[2|\cos \left(\frac{\pi}{K + 2}\right)|\right]~. \label{powerlawquants}
\end{eqnarray}

### 2023-01-13 MCK-manuscript/Supplementary/MCK-supplementary.tex
sir's changes

From these polarised states, one can now calculate the ``excess charge" supplied by the impurity site to the conduction bath in the form of gapless excitations. For this, we first note that the form Eq.~\ref{singlet-chain} of the polarised state shows that all the individual terms in the more explicit form of Eq.~\ref{polarised-state} involve the impurity hybridising with the bath. In Eq.~\ref{polarised-state}, each term of the form \(\ket{\sigma}_d\otimes\ket{\bar\sigma}_l\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}\) participates in exactly one singlet \(\ket{\text{SS}_{d,l}}\) and therefore involves hybridisation between the impurity and only the \(l^\text{th}\) channel. Each such term therefore contributes an excess charge \(n_\text{exc}^{(l)}\) of unity to the \(l^\text{th}\) conduction channel and none to the other channels: \(n_\text{exc}^{(l)} = 1 = 1 - n_\text{exc}^{(l^\prime)}\). The final term \(\ket{\bar\sigma}_d\otimes \ket{\sigma,\sigma,\ldots,\sigma}\) in Eq.~\ref{polarised-state} participates in all \(K\) singlets, and therefore involves hybridisation with all the channels. This term therefore contributes the entire excess charge of unity across all the channels, which results in an excess charge contribution of \(n_\text{exc}^{(l)}=1/K\) to each channel. With these in mind, the total excess charge contributed to each channel from the state in Eq.~\ref{polarised-state} is
\begin{eqnarray}
	n_\text{exc}^{(l)} = \frac{1}{K(1+K)}\left[1 + K^2 \times \frac{1}{K}\right] = \frac{1}{K}
\end{eqnarray}

@@

\subsection{Orthogonality catastrophe in the gapless excitations of the 2CK}
By combining the ground-states of the star graph and the effect of hopping into the remaining lattice, it is possible to demonstrate an orthogonality catastrophe~\cite{anderson1967infrared,varma2002singular} in the new modified ground-state. The full Hilbert space consists of the star graph (formed by the impurity site and the zeroth sites of all channels) and the {\it reduced} conduction bath (formed by sites 1 and beyond in all channels). All terms in the Hamiltonian conserve the total spin \(S_\text{tot}^z = S_d^z + S_0^z + s^z\) composed of the impurity spin \(S_d^z\), the zeroth site spin \(S_0^z = \sum_l S_{0,(l)}^z\) and the spin of the reduced bath \(s^z\). We will work in the \(S_\text{tot}^z = 0\) sector. To construct the non-magnetic ground-states, we will assume the presence of gapless excitations vanishingly close to the Fermi surface in the reduced conduction bath. If \(\ket{\phi}\) represents the filled Fermi volume configuration of all the channels, these excitations can be written as \(\ket{e_\sigma^{(l)}} \equiv e^\dagger_{\sigma,(l)} \ket{\phi} = \sum_{k \in \text{FS}}c^\dagger_{k\sigma,(l)} \ket{\phi}\), where \(l \in \left\{1,2\right\} \) is the channel index. Apart from these states, we have the star graph ground-states at \(S_\text{sg}^z \equiv S_d^z + S_0^z = \pm \frac{1}{2}\): \(\ket{S_\text{sg}^z = \frac{\sigma}{2}} = \frac{1}{\sqrt 6}\left( \ket{\sigma,\sigma,\bar\sigma} + \ket{\sigma,\bar\sigma,\sigma} -2\ket{\bar\sigma,\sigma,\sigma} \right),~ \sigma=\pm 1 \). Within each ket, the three symbols indicate the configuration of the impurity spin, the zeroth site of the first channel and that of the second channel respectively. In the absence of any hopping between the star graph and the reduced conduction bath, the full non-magnetic ground states are then of the form:
\begin{equation}\begin{aligned}
	\ket{l,\sigma} = \ket{S^z_\text{sg}=\frac{-\sigma}{2}}\otimes\ket{e_{\sigma}^{(l)}},~l\in\left\{ 1,2 \right\},~\sigma=\pm 1~.
\end{aligned}\end{equation}
We now introduce the hopping \(H_\text{int}\) between the star graph and the reduced conduction bath,
\begin{equation}\begin{aligned}
	H_\text{int} = -t\frac{1}{\sqrt N}\sum_{k,\sigma,l}\left( c^\dagger_{k\sigma,(l)}c_{0\sigma,(l)} + \text{h.c.} \right)~,
\end{aligned}\end{equation}
and treat it under degenerate perturbation theory. Since all terms in the Hamiltonian conserve the number of particles in each channel, the states with different \(l\) do not mix. For each value of \(l\), the \(2\times 2\) matrix of \(H_\text{int}\) takes the form
\begin{equation}\begin{aligned}
	H_\text{int} = \frac{4t^2}{J^*}\begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix} ~.
\end{aligned}\end{equation}
The non-zero off-diagonal terms arise because of second-order scattering processes.
Diagonalising this gives the modified new ground-states:
\begin{equation}\begin{aligned}
	\ket{\psi_\pm^{(l)}} = \frac{1}{\sqrt 2}\left(\ket{l,\uparrow} \pm \ket{l,\downarrow}\right), E_\pm = -4t^2/J^*~.
\end{aligned}\end{equation}
We can now calculate the residue for scattering processes of the kind \(e^\dagger_{\sigma,(l)} e_{\bar\sigma,(l)}\), in the new ground-state and excited state, and they are found to vanish:
\begin{equation}\begin{aligned}
	Z = |\braket{\psi_+^{(l)}| e^\dagger_{\uparrow,(l)} e_{\downarrow,(l)} | \psi_-^{(l)}}|^2 = \left|\bra{\psi_+^{(l)}}\left(\ket{S_\text{sg}^z=\frac{1}{2}}\ket{e_\uparrow^{(l)}}\right)\right|^2 = 0
\end{aligned}\end{equation}
This shows that the single-particle excitations are no longer long-lived, signaling the orthogonality catastrophe.

>>>>

From these polarised states, one can now calculate the ``excess charge" supplied by the impurity site to the conduction bath in the form of gapless excitations. For this, we first note that the form Eq.~\ref{singlet-chain} of the polarised state shows that all the individual terms in the more explicit form of eq.~\ref{polarised-state} involve the impurity hybridising with the bath. In eq.~\ref{polarised-state}, each term of the form \(\ket{\sigma}_d\otimes\ket{\bar\sigma}_l\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}\) participates in exactly one singlet \(\ket{\text{SS}_{d,l}}\) and therefore involves hybridisation between the impurity and only the \(l^\text{th}\) channel. Each such term therefore contributes an excess charge \(n_\text{exc}^{(l)}\) of unity to the \(l^\text{th}\) conduction channel and none to the other channels: \(n_\text{exc}^{(l)} = 1 = 1 - n_\text{exc}^{(l^\prime)}\). The final term \(\ket{\bar\sigma}_d\otimes \ket{\sigma,\sigma,\ldots,\sigma}\) in Eq.~\ref{polarised-state} participates in all \(K\) singlets, and therefore involves hybridisation with all the channels. This term therefore contributes the entire excess charge of unity across all the channels, which results in an excess charge contribution of \(n_\text{exc}^{(l)}=1/K\) to each channel. With these in mind, the total excess charge contributed to each channel from the state in Eq.~\ref{polarised-state} is
\begin{eqnarray}
	n_\text{exc}^{(l)} = \frac{1}{K(1+K)}\left[1 + K^2 \times \frac{1}{K}\right] = \frac{1}{K}
\end{eqnarray}
This result then connects to the Friedel scattering phase shift (eq.(20) of the main manuscript) and the magnetisation of the impurity (eq.(21) of the main manuscript). In this way, the excess charge $n_\text{exc}^{(l)}$ of the star graph is also observed to guide the RG flow of the MCK problem to the intermediate coupling fixed point (eq.(55) of the main manuscript), and lead to the power-law behaviour of various thermodynamic quantities at the fixed point (eq.(56) of the main manuscript).

@@

\subsection{Orthogonality catastrophe in the gapless excitations of the 2CK}
By combining the ground-states of the star graph and the effect of hopping into the remaining lattice, it is possible to demonstrate an orthogonality catastrophe~\cite{anderson1967infrared,varma2002singular} in the modified ground-state (see also subsection 5.2.3 of the main manuscript for an entanglement based perspective). The full Hilbert space consists of the star graph (formed by the impurity site and the zeroth sites of all channels) and the {\it reduced} conduction bath (formed by sites 1 and beyond in all channels). All terms in the Hamiltonian conserve the total spin \(S_\text{tot}^z = S_d^z + S_0^z + s^z\) composed of the impurity spin \(S_d^z\), the total zeroth site spin \(S_0^z = \sum_l S_{0,(l)}^z\) and the spin of the reduced bath \(s^z\). We will work in the \(S_\text{tot}^z = 0\) sector. To construct the non-magnetic ground-states, we will assume the presence of gapless excitations vanishingly close to the Fermi surface in the reduced conduction bath. If \(\ket{\phi}\) represents the filled Fermi volume configuration of all the channels, these excitations can be written as \(\ket{e_\sigma^{(l)}} \equiv e^\dagger_{\sigma,(l)} \ket{\phi} = \sum_{k \in \text{FS}}c^\dagger_{k\sigma,(l)} \ket{\phi}\), where \(l \in \left\{1,2\right\} \) is the channel index. Apart from these states, we have the star graph ground-states at \(S_\text{sg}^z \equiv S_d^z + S_0^z = \pm \frac{1}{2}\): \(\ket{S_\text{sg}^z = \frac{\sigma}{2}} = \frac{1}{\sqrt 6}\left( \ket{\sigma,\sigma,\bar\sigma} + \ket{\sigma,\bar\sigma,\sigma} -2\ket{\bar\sigma,\sigma,\sigma} \right),~ \sigma=\pm 1 \). Within each ket, the three symbols indicate the configuration of the impurity spin, the zeroth site of the first channel and that of the second channel respectively. In the absence of any hopping between the star graph and the reduced conduction bath, the full non-magnetic ground states are then of the form:
\begin{equation}\begin{aligned}
	\ket{l,\sigma} = \ket{S^z_\text{sg}=\frac{-\sigma}{2}}\otimes\ket{e_{\sigma}^{(l)}},~l\in\left\{ 1,2 \right\},~\sigma=\pm 1~.
\end{aligned}\end{equation}
Using degenerate perturbation theory, we now treat the effects of hopping \(H_\text{int}\) between the star graph and the reduced conduction bath
\begin{equation}\begin{aligned}
	H_\text{int} = -t\frac{1}{\sqrt N}\sum_{k,\sigma,l}\left( c^\dagger_{k\sigma,(l)}c_{0\sigma,(l)} + \text{h.c.} \right)~.
\end{aligned}\end{equation}
Since all terms in the Hamiltonian conserve the number of particles in each channel, the states with different \(l\) do not mix. For each value of \(l\), the \(2\times 2\) matrix of \(H_\text{int}\) takes the form
\begin{equation}\begin{aligned}
	H_\text{int} = \frac{4t^2}{J^*}\begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix} ~,
\end{aligned}\end{equation}
where the non-zero off-diagonal terms arise because of second-order scattering processes. Diagonalising this gives the modified new ground-states:
\begin{equation}\begin{aligned}
	\ket{\psi_\pm^{(l)}} = \frac{1}{\sqrt 2}\left(\ket{l,\uparrow} \pm \ket{l,\downarrow}\right)~,~ E_\pm = -4t^2/J^*~.
\end{aligned}\end{equation}
We can now compute the residue for scattering processes of the kind \(e^\dagger_{\sigma,(l)} e_{\bar\sigma,(l)}\) between the new ground-state and excited state, and display that they vanish identically:
\begin{equation}\begin{aligned}
	Z = |\braket{\psi_+^{(l)}| e^\dagger_{\uparrow,(l)} e_{\downarrow,(l)} | \psi_-^{(l)}}|^2 = \left|\bra{\psi_+^{(l)}}\left(\ket{S_\text{sg}^z=\frac{1}{2}}\ket{e_\uparrow^{(l)}}\right)\right|^2 = 0
\end{aligned}\end{equation}
This shows that the single-particle excitations are no longer long-lived, signalling the orthogonality catastrophe inherent in the intermediate coupling fixed point theory of the MCK.
